\documentclass[11pt]{article}
% Basic environment setup for the document
\title{\textbf{IGVC Report 2026}}
\author{Cornell Electric Vehicles Student Project Team}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{color}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{hyperref}

\hypersetup{colorlinks=true, linkcolor=black,urlcolor=blue}

\begin{document}

% Cover Page 
\maketitle

\newpage

% note: use asterisk for unnumbered sections
\tableofcontents

\newpage

\section{System Requirements and Design}
\subsubsection*{Things to Write}

\begin{itemize}
  \item Describe the system engineering process you followed to identify important System and Subsystem requirements.
  \item List at least 2 requirements for: (a) the mechanical design of your vehicle, (b) safety, (c) the electrical/electronic components
  \item For each challenge you are targeting (AutoNav and SelfDrive), list at least two requirements that guided your design for each of: (a) perception, (b) driving logic, and (c) key performance indicators.
  \item For each requirement you listed (12 for one course, 18 if both) explain what in these rules elsewhere that drives this requirement, describe how you will quantifiably measure the requirement, and set a target value.
\end{itemize}

\section{Mechanical Design}
\subsubsection*{Things to Write}

\begin{itemize}
  \item Describe the mechanical design of your robot, including CAD or other drawings of your vehicle
  \item Describe significant decisions on the frame structure, housing, and/or overall design
  \item Describe significant components of your vehicle’s drive system, electrical power system, and the control system that enables computer-controlled motion. Components acquired ready-made must be identified, but their internal components need not be described in detail.
  \item Describe the significant mechanical components, including the frame, structure, suspension, housing, and weather proofing. Clearly identify the aspects of your mechanical design that are driven by each mechanical system requirement you listed.
  \item For each mechanical requirement you listed, compare the target value with the most recently measured actual value, and discuss what this tells you about your vehicle
\end{itemize}

\section{Safety}
\subsubsection*{Things to Write}

\begin{itemize}
  \item Describe the robot’s safety aspects while being transported, parked, and charging.
  \item Describe the robot’s safety aspects while operating on the course(s), including the mechanical and wireless ESTOP systems.
  \item Clearly identify the aspects of your safety efforts that are driven by each safety requirement you listed.
  \item For each safety requirement you listed, compare the target value with the most recently measured actual value, and discuss what this tells you about your vehicle
\end{itemize}

\section{Electrical/Electronic Design}
\subsubsection*{Things to Write}

\begin{itemize}
  \item Describe significant power, electrical, and electronic components in your vehicle, including electronics, computers, sensors, and motor controllers
  \item Describe significant decisions made in designing/selecting the electrical and electronic components
  \item Describe the power distribution system’s capacity, max. run time, recharge time, and safety
  \item Clearly identify the aspects of your electrical and electronic components that are driven by each electrical/electronic components system requirement you listed.
  \item For each electrical/electronic components system requirement you listed, compare the target value with the most recently measured actual value, and discuss what this tells you about your vehicle
\end{itemize}

\section{Perception}
\subsubsection*{Things to Write}

\begin{itemize}
  \item If you are targeting both challenges, you must include separate discussions of how your perception system matches each course.
  \item Describe processing of the sensor data to identify course features and items around the vehicle, including obstacles and lane markings, and the use of machine vision to perceive the environment.
  \item If targeting AutoNav, describe how the system identifies lanes and obstacles.
  \item If targeting SelfDrive, describe how the vehicle senses pedestrians, stop signs, and road obstacles.
  \item Describe the internal representation of the course built from the perception data which is used by the driving logic. This might be a sophisticated internal representation of the environment or a simple list of features. Include a discussion of how it is created and updated as the robot moves.
  \item Clearly identify how your design of the sensor data processing system was driven by the perception requirements you listed.
  \item For each perception requirement you listed, compare the target value with the most recentlymeasured actual value, and discuss what this tells you about your vehicle
\end{itemize}

\subsubsection*{Obstacle Segmentation}
\begin{itemize}
    \item How LiDAR scan is processed as raw points in PointCloud2 format to clusters in PointCloud2 format w/ clusterids to consistent clusters, birds-eye-view projection, and occupancy grid. The idea eventually is also to incorporate SLAM's output as a preferred (but optional) pre-processing step for LiDAR scans: either clustering takes in raw point cloud directly from the next LiDAR scan or the scan map outputted by SLAM (when we have loop closure). This means that the resulting BEV projection and occupancy grid can either be of one instance or a history of scans. Localization information is also necessary for obstacle tracking, as we want pre-deteremined orientation of the vehicle for static point cloud alignment. Specifically, we want there to be negligible transformation between static points over time, such that obstacle tracking can more accurately determine trajectories of dynamic and moving obstacles. Localization is given either as raw IMU data or as an output of SLAM. Once again, we will fallback to raw IMU data in case SLAM output has high uncertainty, but would preferably rely more on SLAM's output.
    \item LiDAR scan to clusters: this is done either by naive Euclidean or two-layer-graph clustering. 
    \item Naive Euclidean cluster algorithm will iterate through all points of the input point cloud, and attempt growing new clusters starting at unclustered seeds. Only unclustered points that are within a Euclidean distance threshold from the point currently being explored will be added to the same cluster. Given that this is a sequential process that depends on the structure of existing clusters, full parallelization is difficult.
    \item Two-layer-graph clustering takes advantage of the vertical and horizontal angle resolutions of LiDAR hardware for optimization. First segmentation involves clustering points within a threshold along the same horizontal ring (the ray projected from LiDAR origin to point in the same row will share the same vertical angle from the ground plane). This can be parallelized. Each segmentation has a corresponding range graph node that stores the leftmost and rightmost points of that cluster. Second segmentation involves performing BFS on this range graph, merging nodes that are vertically adjacent. We will have to search through all permutations of the range graph for accurate merging, however, given the first segmentation, the size of the range graph is significantly smaller than the total number of points. This is proposed to be linear runtime.
    \item Assuming all clusters outputted are accurate, obstacle tracking constructs a cost matrix populated by how well past and current clusters via oriented bounding box overlap. We run Hungarian Algorithm and max bipartite matching to generate matchings between past and current clusters that minimizes the final cost. These matchings are used to update current clusters with their corresponding past clusters' clusterid. Trajectories of dynamic obstacles will be tracked by viewing the history of position of clusters of the same clusterid. 
    \item Conversion of LiDAR scan to BEV projection and occupancy grid do not require any knowledge of obstacle tracking or clustering. Obstacle segmentation can be viewed as a LiDAR processing step, in which the outputted occupancy grid will be used as input into planning. Occupancy grids of point clouds are also computed based off of the LiDAR's horizontal and vertical angle resolutions, where ray casting and map projection allows point clouds to be projected onto the ground frame. This projection is essentially BEV projection. 
\end{itemize}
\section{Driving Logic}
\subsubsection*{Things to Write}

\begin{itemize}
  \item If you are targeting both challenges, you must include separate discussions of how your driving logic matches each course.
  \item Design of the lane following and obstacle avoidance systems must be specifically described, along with how the vehicle navigates through its environment. Describe how the system uses GPS for waypoint navigation and localization.
  \item If targeting AutoNav, describe how your robot uses the perception system’s output and other information to follow lanes, detect and avoid obstacles, climb the ramp, and navigate to the GPS waypoints. Include how vehicle motion is generated and monitored to move the vehicle through the course, including how it deals with complex obstacles including switchbacks and center islands dead ends, traps, and potholes.
  \item If targeting SelfDrive, describe how the vehicle uses the perception system’s output and otherinformation to follow the rules of the road while navigating the course that includes pedestrians,stop signs, road obstacles, and other items.
  \item Clearly identify how your design was driven by the driving logic requirements you listed.
  \item For each driving logic requirement you listed, compare the target value with the most recentlymeasured actual value, and discuss what this tells you about your vehicle
\end{itemize}

\section{Key Performance Indicators}
\subsubsection*{Things to Write}

\begin{itemize}
  \item If you are targeting both challenges, you must include separate discussions for each course.
  \item Describe how you will measure each of the key performance indicators you selected to check that your robot is competitive on the target course(s), what value/result you are targeting, and how you selected that value/result for the KPI.
  \item For each KPI requirement you listed, compare the target value with the most recently measured actual value, and discuss what this tells you about your vehicle
\end{itemize}

\section{Analysis of Complete Vehicle}
\subsubsection*{Things to Write}

\begin{itemize}
  \item Describe lessons learned during construction and system integration
  \item Identify key mechanical and electrical components that have failed during testing and discuss what changes you made to prevent repeat failures. Did your changes prevent repeat failures?
  \item Describe your software testing, bug tracking, and version control processes
  \item Describe your simulation-based testing process (e.g., Gazebo, etc.)
  \item Describe physical testing to date (mechanical, electronic, indoors, real world, etc.) and identifykey differences in actual performance compared to predictions from simulation.
\end{itemize}

\section{Cyber Security Analysis}
\subsubsection*{Things to Write}

\begin{itemize}
  \item Modern robotic and human driven vehicles are network-connected, contain large amounts of software from multiple vendors, and are an inviting target for cyber-attacks.
  \item List 3 cyber vulnerabilities present in your vehicle and discuss what steps should be taken to harden/remove them before it enters series production and is widely deployed.
\end{itemize}

\end{document}
