\section{Driving Logic}
% \subsubsection*{Things to Write}
%
% \begin{itemize}
%   \item If you are targeting both challenges, you must include separate discussions of how your driving logic matches each course.
%   \item Design of the lane following and obstacle avoidance systems must be specifically described, along with how the vehicle navigates through its environment. Describe how the system uses GPS for waypoint navigation and localization.
%   \item If targeting AutoNav, describe how your robot uses the perception system’s output and other information to follow lanes, detect and avoid obstacles, climb the ramp, and navigate to the GPS waypoints. Include how vehicle motion is generated and monitored to move the vehicle through the course, including how it deals with complex obstacles including switchbacks and center islands dead ends, traps, and potholes.
%   \item If targeting SelfDrive, describe how the vehicle uses the perception system’s output and otherinformation to follow the rules of the road while navigating the course that includes pedestrians,stop signs, road obstacles, and other items.
%   \item Clearly identify how your design was driven by the driving logic requirements you listed.
%   \item For each driving logic requirement you listed, compare the target value with the most recentlymeasured actual value, and discuss what this tells you about your vehicle
% \end{itemize}

\subsection{Extended Kalman Filter}

Our vehicle makes use of a \textbf{custom Extended Kalman Filter (EKF)} to estimate the vehicle's state. For the general kinematics, the state is defined as:
\begin{equation}
\mathbf{x}=
\begin{bmatrix}
p_W \in \mathbb{R}^3 \\
R_{WB} \in SO(3) \\
v_W \in \mathbb{R}^3 \\
\omega_B \in \mathbb{R}^3 \\
\Omega_W \in \mathbb{R}^4
\end{bmatrix}
\end{equation}

However, due to the group $SO(3)$ being a \textit{non-Euclidean manifold}, this means that we cannot simply add or subtract orientation errors like the other states. This means that we need a local linear space, which is provided by the lie algebra $\mathfrak{so}(3)$, which is the tangent space of $SO(3)$. This allows us to define the error state as:

\begin{equation}
\delta{\mathbf{x}} =
\begin{bmatrix}
\delta{p_W} \in \mathbb{R}^3 \\
\delta\theta \in \mathfrak{so}(3) \\ \delta{v_W} \in \mathbb{R}^3 \\
\delta{\omega_B} \in \mathbb{R}^3 \\
\delta{\Omega_W} \in \mathbb{R}^4
\end{bmatrix}
\end{equation}

This means that we can formulate the rotation update in error space as $\keepmath{R^+=R_\mathrm{nom} \exp(\delta \theta^\times)}$ which makes use of the Rodrigues' formula (using $\keepmath{\exp(\delta \theta^\times)\approx I + \delta \theta^\times}$ for small angle changes) to compute the exponential map from $\mathfrak{so}(3)$ to $SO(3)$. This allows us to properly handle the non-linearities of the orientation state in our EKF, ensuring accurate state estimation for our vehicle.

Another unique aspect of the filter is that the $F$ and $G$ linearization matrices are computed using automatic differentiation via \texttt{JAX}. This is due to the complex dynamics formulated for the vehicle, which include non-linear slip and contact tire models, and full rigid body dynamics of the entire vehicle, including tire spin as exponential decay. 

Combining all of these formulations, we can write out the predict step as:

\begin{equation}
  \begin{gathered}
    \hbf{x}_{k+1|k} = f(\hbf{x}_{k|k},\mathbf{u}_k,\Delta t) \\
    P_{k+1|k} = F_k P_{k|k} F_k^\top + Q
  \end{gathered}
\end{equation}
And the update state as:
\begin{equation}
  \begin{gathered}
    \hbf{x}_{k+1|k+1} = \hbf{x}_{k+1|k} + K_k (\mathbf{z}_k - h(\hbf{x}_{k+1|k})) \\
    \beta = I - K_k H_k \implies P_{k+1|k+1} = \beta P_{k+1|k} \beta^\top \\
    + K_k R K_k^\top
  \end{gathered}
\end{equation}

The full dynamics are formulated at \href{https://github.com/cornellev/ackermann-jax}{this repository}. These are then also fed into a custom Model Predictive Control (MPC) model, which is detailed in the next subsection.


\subsection{Model Predictive Control}

Using the Jacobians formulated from the Extended Kalman Filter, we assmeble the following prediction equation in error state:

\begin{equation}
  \delta \mathbf{x}_{k+1} \approx F_k \delta \mathbf{x}_k + G_k \delta \mathbf{u}_k
\end{equation}

where $G_k$ is the Jacobian of the dynamics with respect to the control input. From this, we can stack the linearized dynamics over a horizon $N$ into the state and control histories, defined as:

\begin{equation}
  \mathbf{X} = \begin{bmatrix} \delta\mathbf{x}_1 \\ \vdots \\ \delta\mathbf{x}_N\end{bmatrix} \in \mathbb{R}^{16N}, \mathbf{U} = \begin{bmatrix} \delta\mathbf{u}_0 \\ \vdots \\ \delta\mathbf{u}_{N-1}\end{bmatrix} \in \mathbb{R}^{3N}
\end{equation}

This is inserted into the standard lifted form, defined as:

\begin{equation}
  \mathbf{X} = \Phi \delta\mathbf{x}_0 + \Theta \mathbf{U}
\end{equation}

where:

\begin{equation}
  \begin{gathered}
    \Phi = \begin{bmatrix} F_0 \\ F_1 F_0 \\ \vdots \\ F_{N-1} \cdots F_0 \end{bmatrix}\\ 
    \Theta=\left[\begin{array}{ccc}
      G & & \\
      F G & G & \\
      F^2 G & F G & G \\
      \vdots & & \ddots
    \end{array}\right]
  \end{gathered}
\end{equation}

This formulation allows us to write the entire trajectory as a \textit{linear function} of the initial error and the control input, which collapses the MPC problem into a single \textbf{quadratic program} (QP). We formulate the quadratic cost $J$ as:

\begin{equation}
  \resizebox{\linewidth}{!}{%
    $J=\mathbf{U}^{\top}\left(\Theta^{\top} \bar{Q} \Theta+\bar{R}\right) \mathbf{U}+2\left(\Theta^{\top} \bar{Q} \Phi \delta \mathbf{x}_0\right)^{\top} \mathbf{U}+\dots$
  }
\end{equation}

Where $\bar{Q}=\mathrm{blkdiag}(Q,\dots,Q,P_f)$ and $\bar{R}=\mathrm{blkdiag}(R,\dots,R,P_f)$, and we omit the terminal cost weighting $\delta \mathbf{x}_N^\top P_f \delta\mathbf{x}_N$ for brevity.

Finally, this culminates in solving for the optimal $\mathbf{U}$ history via a QP as the following:

\begin{equation}
  \begin{gathered}
  \mathbf{U}_\mathrm{opt} = \underset{\mathbf{U}}{\mathrm{argmin}}\  \mathbf{U}^\top H \mathbf{U}+2 f^\top \mathbf{U} \\
  \mathrm{s.t.} \quad A\mathbf{u} \leq \mathbf{b}
\end{gathered}
\end{equation}

Where $A$ and $b$ are constriant matrices that allow us to control various aspects of the controller to fit our system. This is included in the same repository as above, and allows for simultaneous execution of both the localization and control frameworks into a single package. Furthermore, this allows us to have a robust control algorithm that requires little to no hand tuning of the controller, but rather tuning the dynamics themselves to ensure that the physical qunatities are represented properly.
